Comparison of Catalogs

### 2024-07-30 compare/compare.qmd
SFR KDE

If we use the decimal logarithm of the data we can clearly see the linear correlation.

@@

```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True)
plt.show()

```
:::

>>>>

@@

```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True)
plt.show()
```

## Density Grids

```{python}
# Create a pair grid 
sns.pairplot(sfr_data, corner=True, kind="kde", diag_kind="hist")
plt.show()
```

:::
